Interval Probability for Fuzzy Quantum Theories

### 2016-06-13 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} updates...

%%%%%
\subsection{Measuring Quantum Probabilities}
\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

>>>>

%%%%%
\subsection{Measuring Quantum Probabilities}

If we adopt the frequency interpretation as in section~\ref{subsec:Measuring-Probabilities:-Buffon},
and measure the angular momentum for a spin-one particle in the Stern-Gerlach
experiment~\cite{FeynmanLeightonSands1965,Stern1988,peres1995quantum,544199}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, three spots will be produced
corresponding to $\ket{+Z}$, $\ket{0Z}$, and $\ket{-Z}$. In reality,
the local field strength cannot prefect directs to to the $z$-axis,
and all particles come from a hot oven cannot have the same velocity.
As the result, spots will be broader and more washed out so that it
may sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$. About the imperfect direction of
field strength, we might take it into account when we introduce the
discrete quantum theory later.

\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}
